\centerline{\bf References}

\bigskip

{\frenchspacing

\item{[1]}
K. Amano, S. Hataki and S. Maeda,
A text converter src2tex : Basic, C, C++, Fortran, Lisp, Pascal {\tt ->} \TeX
\quad ({\sl to appear\/}).

\item{[2]}
R. Baecker and A. Marcus,
Human Factors and Typography for More Readable Programs,
{\sl Addison-Wesley, Reading, MA}, 1990.

\item{[3]}
J. December,
Presenting Java,
{\sl Sams.Net Publishing}, 1995.

\item{[4]}
J. W. Eaton,
Octave: A High-Level Interactive Language for Numerical Computations,
Edition 1.1 for Octave version 1.1.1, 1995.

\item{[5]}
B. Fuchssteiner and others,
MuPAD Multi Processing Algera Data Tool User's Manual Draft Version,
{\sl Bennon Fuchssteiner, Automath,
University of Paderborn, Paderborn, Germany}, 1992-95.

\item{[6]}
A. C. Hearn,
REDUCE User's Manual, version 3.5,
{\sl RAND Publication}, CP78(Rev. 7/94), 1994.

\item{[7]}
B. W. Kernighan and D. M. Ritchie,
The C Programming Language,
{\sl Prentice Hall}, 1978.

\item{[8]}
D. E. Knuth,
Literate Programming,
{\sl The Computer Journal},
{\bf 27} (1984), 97-111.

\item{[9]}
D. E. Knuth,
The {\TeX}book,
{\sl Addison-Wesley}, 1984.

\item{[10]}
P. Mohseni,
Maple in Action,
An Introductory Handbook,
{\sl Iowa State University}, 1995.

\item{[11]}
M. Noro and T. Shimoyama,
Asir User's Manual, Edition 2.0 for Asir-940420,
{\sl Fujitsu Laboratories Ltd.}, 1994.

\item{[12]}
J. K. Ousterhout,
Tcl and Tk Toolkit,
Addison Wesley Publishing Company, Inc., 1993.

\item{[13]}
K. Sigmon,
MATLAB Primer, Second Edition,
{\sl University of Florida}, 1992.

\item{[14]}
G. L. Steele Jr.,
Common Lisp The Language, 2nd edition,
{\sl Digital Equipment Corporation}, 1990.

\item{[15]}
D. B. Thompson,
The Literate Programming Frequently Asked Questions List,
{\sl comp.programming. literate newsgroup}, 1995.

\item{[16]}
S. Wolfram,
Mathematica,
A System Doing Mathematics by Computer, Second Edition,
{\sl Wolfram Research}, Inc., \rm 1992.

}
